---
title: "Ethical Preferences for the Fair Allocation of Resources in the Moral Dilemma of Triage"
author: "Peer Keßler and Ivar Krumpal"
output: html_notebook
---

# Packages

```{r}

## Uncomment for installing packages. ##

# install.packages("janitor")
# install.packages("lme4")
# install.packages("lmerTest")
# install.packages("lubridate")
# install.packages("magrittr")
# install.packages("tidyverse")


library(janitor)
library(lme4)
library(lmerTest)
library(lubridate)
library(countrycode)
library(magrittr)
library(tidyverse)

sessionInfo()
```

# Versions:

R version 4.3.1 (2023-06-16)
Platform: aarch64-apple-darwin20 (64-bit)
Running under: macOS Sonoma 14.2.1

Matrix products: default
BLAS:   /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib 
LAPACK: /Library/Frameworks/R.framework/Versions/4.3-arm64/Resources/lib/libRlapack.dylib;  LAPACK version 3.11.0

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

time zone: Europe/Berlin
tzcode source: internal

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] forcats_1.0.0     stringr_1.5.0     dplyr_1.1.3       purrr_1.0.2       readr_2.1.4      
 [6] tidyr_1.3.0       tibble_3.2.1      ggplot2_3.4.3     tidyverse_2.0.0   magrittr_2.0.3   
[11] countrycode_1.5.0 lubridate_1.9.3   lmerTest_3.1-3    lme4_1.1-34       Matrix_1.6-1.1   
[16] janitor_2.2.0    

loaded via a namespace (and not attached):
 [1] utf8_1.2.3          generics_0.1.3      stringi_1.7.12      lattice_0.21-8     
 [5] hms_1.1.3           grid_4.3.1          timechange_0.2.0    fansi_1.0.5        
 [9] scales_1.2.1        numDeriv_2016.8-1.1 cli_3.6.1           rlang_1.1.1        
[13] munsell_0.5.0       splines_4.3.1       withr_2.5.1         tools_4.3.1        
[17] tzdb_0.4.0          nloptr_2.0.3        minqa_1.2.6         colorspace_2.1-0   
[21] boot_1.3-28.1       vctrs_0.6.4         R6_2.5.1            lifecycle_1.0.3    
[25] snakecase_0.11.1    MASS_7.3-60         pkgconfig_2.0.3     pillar_1.9.0       
[29] gtable_0.3.4        glue_1.6.2          Rcpp_1.0.11         xfun_0.40          
[33] tidyselect_1.2.0    rstudioapi_0.15.0   knitr_1.44          nlme_3.1-162       
[37] compiler_4.3.1   

# Read data

```{r}
triage_data <- dget(file = "data/data.R")
```

# Clean data

```{r}
triage_data_clean <-
  triage_data %>% 
  filter(bot_all, time >= 5)
```

# Plots

## Plot a

```{r}
triage_data_clean %>% 
   filter(vig_set <= 5) %>% 
  lmer(formula = vig_choice ~ vig_weight + vig_age + vig_chance_of_survival_with_ventilation + vig_ventilation_status + vig_children + vig_disability + vig_volunteer_work + vig_vaccination_status + (1|id),
       data = .) %>% 
  confint(object = .,
          method = "Wald") %>% 
  as.data.frame() %>% 
  as_tibble(.,
            rownames = "attr") %>% 
  filter(str_detect(string = attr,
                    pattern = "vig_")) %>% 
  clean_names() %>% 
  add_case(attr = c("20% chance of survival (Ref.)",
                    "25 years old (Ref.)"
                    )) %>% 
  mutate(effect = x2_5_percent + (x97_5_percent - x2_5_percent) / 2,
         attr = str_extract(attr, "[A-Z0-9].*"),
         attr = factor(attr,
                       levels = c("20% chance of survival (Ref.)",
                                  "50% chance of survival",
                                  "80% chance of survival",
                                  "25 years old (Ref.)",
                                  "50 years old",
                                  "75 years old",
                                  "Is already ventilated",
                                  "Is vaccinated",
                                  "Has children",
                                  "Has a disability",
                                  "Does volunteer work",
                                  "Overweight"
                                  )
                       ),
         attr = fct_rev(attr),
         effect = if_else(is.na(effect),
                          true = 0,
                          false = effect)
         ) %>% 
  ggplot(mapping = aes(y = effect,
                       x = attr,
                       ymin = x2_5_percent,
                       ymax = x97_5_percent)) +
  geom_hline(yintercept = 0,
             alpha = 0.6) +
  geom_errorbar(width = 0.35,
                color = "#27363A") + 
  geom_point(size = 2.5,
             color = "#EB8019") +
  coord_flip() +
  labs(x = "",
       y = "AMCE",
       title = "a)") + 
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        plot.title.position = "plot")
```

Corresponding regression table:

```{r}
triage_data_clean %>% 
   filter(vig_set <= 5) %>% 
  lmer(formula = vig_choice ~ vig_weight + vig_age + vig_chance_of_survival_with_ventilation + vig_ventilation_status + vig_children + vig_disability + vig_volunteer_work + vig_vaccination_status + (1|id),
       data = .) %>% 
  summary()
```

## Plot b

```{r}
triage_data_clean %>%
  select(id, contains("proc_")) %>%
  distinct() %>% 
  summarise(across(contains("proc_"), 
                   list(mean = ~mean(., na.rm = TRUE),
                        sd = ~sd(., na.rm = TRUE)
                        ), 
                   .names = "{.col}_{.fn}"
                   ),
            n = n()) %>%
  pivot_longer(cols = -n, 
               names_to = c(".value", "Procedure"), 
               names_sep = "_", 
               values_drop_na = TRUE) %>%
  mutate(Procedure = factor(str_replace(Procedure, "proc_", ""), 
                            levels = c("maxprog", "fcfs", "random", "benpast", "benfut", "sick", "young", "lifeq"), 
                            labels = c("Maximize prognosis", "First-come, first-served", "Random selection", 
                                       "Benefit in the past", "Benefit in the future", "Sickest first", 
                                       "Youngest first", "Life quality after recovery")),
         Procedure = fct_rev(Procedure)) %>%
  group_by(Procedure) %>%
  mutate(e = qt(0.975, df = first(n) - 1) * nth(proc, n = 2) / sqrt(first(n)), 
         upper = first(proc) + e, 
         lower = first(proc) - e,
         proc = first(proc)) %>%
  ungroup() %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = Procedure,
                       y = proc,
                       ymin = lower,
                       ymax = upper
                       )
         ) +
  geom_bar(stat = "identity",
             fill = "#EB8019") +
  geom_errorbar(width = 0.35,
                color = "#27363A") + 
  coord_flip() +
  labs(x = "",
       y = "Mean rating of procedures",
       title = "b)") +
  scale_y_continuous(breaks = 1:6,
                     limits = c(0,6)) +
  theme_minimal() +
  theme(text = element_text(family = "serif",),
        plot.title.position = "plot")
```

Additional stats:

```{r}
triage_data_clean %>%
  select(id, contains("proc_")) %>%
  distinct() %>% 
  summarise(across(contains("proc_"), 
                   list(mean = ~mean(., na.rm = TRUE),
                        sd = ~sd(., na.rm = TRUE)
                        ), 
                   .names = "{.col}_{.fn}"
                   ),
            n = n()) %>%
  pivot_longer(cols = -n, 
               names_to = c(".value", "Procedure"), 
               names_sep = "_", 
               values_drop_na = TRUE) %>%
  mutate(Procedure = factor(str_replace(Procedure, "proc_", ""), 
                            levels = c("maxprog", "fcfs", "random", "benpast", "benfut", "sick", "young", "lifeq"), 
                            labels = c("Maximize prognosis", "First-come, first-served", "Random selection", 
                                       "Benefit in the past", "Benefit in the future", "Sickest first", 
                                       "Youngest first", "Life quality after recovery")),
         Procedure = fct_rev(Procedure),
         value = rep(c("M","SD"), times = length(unique(.$Procedure))
                     )
         )
```

## Plot c

```{r}
triage_data_clean %>% 
  filter(vig_set <= 5) %>% 
  mutate(across(contains("proc_"), 
                .fns = ~ if_else(.x <= 4,
                                 "Low",
                                 "High"),
                .names = "{.col}_bi"
                ),
         across(.cols = contains("_bi"),
                .fns = ~ factor(.,
                                levels = c("Low", "High")
                                )
                )
         ) %>% 
  lmer(formula = vig_choice ~ vig_weight * proc_lifeq_bi + vig_age * proc_young_bi + vig_chance_of_survival_with_ventilation * proc_maxprog_bi + vig_chance_of_survival_with_ventilation * proc_sick_bi + vig_ventilation_status * proc_fcfs_bi + vig_children * proc_benfut_bi + vig_disability * proc_lifeq_bi + vig_volunteer_work  * proc_benpast_bi + vig_vaccination_status * proc_benpast_bi + (1|id),
       data = .) %>% 
  confint(object = .,
          method = "Wald") %>% 
   as.data.frame() %>% 
   as_tibble(.,
             rownames = "attr") %>% 
   filter(str_detect(string = attr,
                     pattern = ":")) %>% 
   clean_names() %>% 
   mutate(attr = factor(attr, 
                        levels = c("vig_chance_of_survival_with_ventilation50% chance of survival:proc_maxprog_biHigh",
                                   "vig_chance_of_survival_with_ventilation80% chance of survival:proc_maxprog_biHigh",
                                   "vig_chance_of_survival_with_ventilation50% chance of survival:proc_sick_biHigh",
                                   "vig_chance_of_survival_with_ventilation80% chance of survival:proc_sick_biHigh",
                                   "vig_age50 years old:proc_young_biHigh",
                                   "vig_age75 years old:proc_young_biHigh",
                                   "vig_ventilation_statusIs already ventilated:proc_fcfs_biHigh",
                                   "proc_benpast_biHigh:vig_vaccination_statusIs vaccinated",
                                   "vig_volunteer_workDoes volunteer work:proc_benpast_biHigh",
                                   "vig_childrenHas children:proc_benfut_biHigh",
                                   "proc_lifeq_biHigh:vig_disabilityHas a disability",
                                   "vig_weightOverweight:proc_lifeq_biHigh"
                                   ),
                        labels = c("50% chance of survival x Maximize prognosis",
                                   "80% chance of survival x Maximize prognosis",
                                   "50% chance of survival x Sickest first",
                                   "80% chance of survival x Sickest first",
                                   "50 years old x Youngest first",
                                   "75 years old x Youngest first",
                                   "Is already ventilated x First Come, first served",
                                   "Is vaccinated x Benefit in the past",
                                   "Does volunteer work x Benefit in the past",
                                   "Has children x Benefit in the future",
                                   "Has a disability x Life quality after recovery",
                                   "Is overweight x Life quality after recovery")
                        ),
          eff = x97_5_percent - ((x97_5_percent - x2_5_percent) / 2),
          attr = fct_rev(attr)
          ) %>% 
  ggplot(mapping = aes(x = attr,
                       y = eff,
                       ymin = x2_5_percent,
                       ymax = x97_5_percent
                       )
         ) +
    geom_bar(stat = "identity",
             fill = "#EB8019") + 
    geom_errorbar(width = 0.35,) +
    geom_hline(yintercept = 0,
               linetype = "dashed") +
    labs(y = "Interaction effects",
         x = "",
         title = "c)") +
    coord_flip() +
    theme_minimal() +
    theme(text = element_text(family = "serif"),
          plot.title.position = "plot"
          )
```

Corresponding regression table:

```{r}
triage_data_clean %>% 
  filter(vig_set <= 5) %>% 
  mutate(across(contains("proc_"), 
                .fns = ~ if_else(.x <= 4,
                                 "Low",
                                 "High"),
                .names = "{.col}_bi"
                ),
         across(.cols = contains("_bi"),
                .fns = ~ factor(.,
                                levels = c("Low", "High")
                                )
                )
         ) %>% 
  lmer(formula = vig_choice ~ vig_weight * proc_lifeq_bi + vig_age * proc_young_bi + vig_chance_of_survival_with_ventilation * proc_maxprog_bi + vig_chance_of_survival_with_ventilation * proc_sick_bi + vig_ventilation_status * proc_fcfs_bi + vig_children * proc_benfut_bi + vig_disability * proc_lifeq_bi + vig_volunteer_work  * proc_benpast_bi + vig_vaccination_status * proc_benpast_bi + (1|id),
       data = .) %>% 
  summary() 
```

## Plot d

```{r}
triage_data_random <-
  triage_data_clean %>%
  filter(vig_set > 5) %>% 
  group_by(id, vig_set) %>% 
  summarize(random = max(vig_choice)) %>% 
  ungroup() %>% 
  mutate(random = if_else(condition = random == 3,
                          true = 1,
                          false = 0
                          )
         ) %>% 
  group_by(id) %>% 
  summarise(rand_prob = mean(random, na.rm = T))

plot_data <- 
  triage_data_clean %>% 
  select("id","proc_random") %>% 
  distinct() %>% 
  right_join(triage_data_random,
             by = "id") 

predict_data <- 
  tibble(proc_random = 0:7)

predict_data$rand_prob <- 
  plot_data %>% 
  lm(rand_prob ~ proc_random,
     data = .) %>% 
  predict(.,
          newdata = predict_data)

{set.seed(567)
plot_data %>% 
  ggplot(mapping = aes(x = proc_random,
                       y = rand_prob)) +
  geom_jitter(width = 1,
              height = 0.1,
              alpha = 0.5,
              color = "#EB8019") +
  geom_line(data = predict_data,
            mapping = aes(x = proc_random,
                          y = rand_prob),
            color = "#27363A",
            linetype = "dashed",
            linewidth = 0.8) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0,1,0.2)) +
  scale_x_continuous(breaks = 1:6) +
  labs(y = expression(atop("Relative frequency of choosing ", paste(italic("Random selection")))),
       x =  expression(atop("Rated fairness of procedure ", paste(italic("Random selection")))),
       title = "d)") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        plot.title.position = "plot")
}
```

Corresponding regression table:

```{r}
triage_data_random <-
  triage_data_clean %>%
  filter(vig_set > 5) %>% 
  group_by(id, vig_set) %>% 
  summarize(random = max(vig_choice)) %>% 
  ungroup() %>% 
  mutate(random = if_else(condition = random == 3,
                          true = 1,
                          false = 0
                          )
         ) %>% 
  group_by(id) %>% 
  summarise(rand_prob = mean(random, na.rm = T))

plot_data <- 
  triage_data_clean %>% 
  select("id","proc_random") %>% 
  distinct() %>% 
  right_join(triage_data_random,
             by = "id") 

lm(rand_prob ~ proc_random,
     data = plot_data) %>% 
  summary()
```

Additional statistics:

```{r}
triage_data_clean %>% 
  filter(vig_set > 5) %>% 
  group_by(id) %>% 
  mutate(random = if_else(any(vig_choice == 3),
                          true = 1,
                          false = 0)
         ) %>% 
  ungroup() %>% 
 select("id","random") %>% 
  distinct() %>% 
  count(random) %>% 
  mutate(sum = sum(n),
         prop = n/sum)

# 61% of all participants chose "random selection at least once.


triage_data_clean %>% 
  filter(vig_set > 5) %>% 
  transmute(random = if_else(vig_choice == 3,
                          true = 1,
                          false = 0)
         ) %>% 
  count(random) %>% 
  mutate(sum = sum(n),
         prop = n/sum)

#> In 75.6% of all choice sets that include the "random-selection" option the 
#> participants chose to make a deliberate decision instead of using a random 
#> allocation mechanism.

triage_data_random <-
  triage_data_clean %>%
  filter(vig_set > 5) %>% 
  group_by(id, vig_set) %>% 
  summarize(random = max(vig_choice)) %>% 
  ungroup() %>% 
  mutate(random = if_else(condition = random == 3,
                          true = 1,
                          false = 0
                          )
         ) %>% 
  group_by(id) %>% 
  summarise(rand_prob = mean(random, na.rm = T))

plot_data <- 
  triage_data_clean %>% 
  select("id","proc_random") %>% 
  distinct() %>% 
  right_join(triage_data_random,
             by = "id")
plot_data %$%
  cor.test(proc_random,
           rand_prob,
           method = "kendall")
```

# Robustness Checks for Plot c

## Median Split

```{r}
triage_data_clean %>% 
   filter(vig_set <= 5) %>% 
  mutate(proc_maxprog_bi = if_else(proc_maxprog <= median(.$proc_maxprog, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_fcfs_bi = if_else(proc_fcfs <= median(.$proc_fcfs, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_random_bi = if_else(proc_random <= median(.$proc_random, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_benpast_bi = if_else(proc_benpast <= median(.$proc_benpast, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_benfut_bi = if_else(proc_benfut <= median(.$proc_benfut, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_sick_bi = if_else(proc_sick <= median(.$proc_sick, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_young_bi = if_else(proc_young <= median(.$proc_young, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_lifeq_bi = if_else(proc_lifeq <= median(.$proc_lifeq, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         across(.cols = contains("_bi"),
                .fns = ~ factor(.,
                                levels = c("Low", "High")
                                )
                )
         ) %>% 
  lmer(formula = vig_choice ~ vig_weight * proc_lifeq_bi + vig_age * proc_young_bi + vig_chance_of_survival_with_ventilation * proc_maxprog_bi + vig_chance_of_survival_with_ventilation * proc_sick_bi + vig_ventilation_status * proc_fcfs_bi + vig_children * proc_benfut_bi + vig_disability * proc_lifeq_bi + vig_volunteer_work * proc_benpast_bi + vig_vaccination_status * proc_benpast_bi + (1|id),
       data = .) %>% 
  confint(object = .,
          method = "Wald") %>% 
   as.data.frame() %>% 
   as_tibble(.,
             rownames = "attr") %>% 
   filter(str_detect(string = attr,
                     pattern = ":")) %>% 
   clean_names() %>% 
   mutate(attr = factor(attr, 
                        levels = c("vig_chance_of_survival_with_ventilation50% chance of survival:proc_maxprog_biHigh",
                                   "vig_chance_of_survival_with_ventilation80% chance of survival:proc_maxprog_biHigh",
                                    "vig_chance_of_survival_with_ventilation50% chance of survival:proc_sick_biHigh",
                                   "vig_chance_of_survival_with_ventilation80% chance of survival:proc_sick_biHigh",
                                   "vig_age50 years old:proc_young_biHigh",
                                   "vig_age75 years old:proc_young_biHigh",
                                   "vig_ventilation_statusIs already ventilated:proc_fcfs_biHigh",
                                   "proc_benpast_biHigh:vig_vaccination_statusIs vaccinated",
                                   "vig_volunteer_workDoes volunteer work:proc_benpast_biHigh",
                                   "vig_childrenHas children:proc_benfut_biHigh",
                                   "proc_lifeq_biHigh:vig_disabilityHas a disability",
                                   "vig_weightOverweight:proc_lifeq_biHigh"
                                   ),
                        labels = c("50% chance of survival x Maximize prognosis",
                                   "80% chance of survival x Maximize prognosis",
                                   "50% chance of survival x Sickest first",
                                   "80% chance of survival x Sickest first",
                                   "50 years old x Youngest first",
                                   "75 years old x Youngest first",
                                   "Is already ventilated x First Come, first served",
                                   "Is vaccinated x Benefit in the past",
                                   "Does volunteer work x Benefit in the past",
                                   "Has children x Benefit in the future",
                                   "Has a disability x Life quality",
                                   "Is overweight x Life quality")
                        ),
          eff = x97_5_percent - ((x97_5_percent - x2_5_percent) / 2),
          attr = fct_rev(attr)
          ) %>% 
  ggplot(mapping = aes(x = attr,
                       y = eff,
                       ymin = x2_5_percent,
                       ymax = x97_5_percent
                       )
         ) +
    geom_bar(stat = "identity",
             fill = "#EB8019") + 
    geom_errorbar(width = 0.35,) +
    geom_hline(yintercept = 0,
               linetype = "dashed") +
    labs(y = "Interaction effects",
         x = "",
         title = "Plot c with Median Split"
         ) +
    coord_flip() +
    theme_minimal() +
    theme(text = element_text(family = "serif"),
          plot.title.position = "plot"
          )
```

Corresponding regression table:

```{r}
triage_data_clean %>% 
   filter(vig_set <= 5) %>% 
  mutate(proc_maxprog_bi = if_else(proc_maxprog <= median(.$proc_maxprog, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_fcfs_bi = if_else(proc_fcfs <= median(.$proc_fcfs, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_random_bi = if_else(proc_random <= median(.$proc_random, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_benpast_bi = if_else(proc_benpast <= median(.$proc_benpast, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_benfut_bi = if_else(proc_benfut <= median(.$proc_benfut, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_sick_bi = if_else(proc_sick <= median(.$proc_sick, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_young_bi = if_else(proc_young <= median(.$proc_young, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         proc_lifeq_bi = if_else(proc_lifeq <= median(.$proc_lifeq, na.rm = T),
                                  true = "Low",
                                  false = "High"
                                  ),
         across(.cols = contains("_bi"),
                .fns = ~ factor(.,
                                levels = c("Low", "High")
                                )
                )
         ) %>% 
  lmer(formula = vig_choice ~ vig_weight * proc_lifeq_bi + vig_age * proc_young_bi + vig_chance_of_survival_with_ventilation * proc_maxprog_bi + vig_chance_of_survival_with_ventilation * proc_sick_bi + vig_ventilation_status * proc_fcfs_bi + vig_children * proc_benfut_bi + vig_disability * proc_lifeq_bi + vig_volunteer_work * proc_benpast_bi + vig_vaccination_status * proc_benpast_bi + (1|id),
       data = .) %>% 
  summary()
```


## Numeric Value

```{r}
triage_data_clean %>% 
   filter(vig_set <= 5) %>% 
  lmer(formula = vig_choice ~ vig_weight * proc_lifeq + vig_age * proc_young + vig_chance_of_survival_with_ventilation * proc_maxprog + vig_chance_of_survival_with_ventilation * proc_sick + vig_ventilation_status * proc_fcfs + vig_children * proc_benfut + vig_disability * proc_lifeq + vig_volunteer_work * proc_benpast + vig_vaccination_status * proc_benpast + (1|id),
       data = .) %>% 
  confint(object = .,
          method = "Wald") %>% 
   as.data.frame() %>% 
   as_tibble(.,
             rownames = "attr") %>% 
   filter(str_detect(string = attr,
                     pattern = ":")) %>% 
   clean_names() %>% 
   mutate(attr = factor(attr, 
                        levels = c("vig_chance_of_survival_with_ventilation50% chance of survival:proc_maxprog",
                                   "vig_chance_of_survival_with_ventilation80% chance of survival:proc_maxprog",
                                    "vig_chance_of_survival_with_ventilation50% chance of survival:proc_sick",
                                   "vig_chance_of_survival_with_ventilation80% chance of survival:proc_sick",
                                   "vig_age50 years old:proc_young",
                                   "vig_age75 years old:proc_young",
                                   "vig_ventilation_statusIs already ventilated:proc_fcfs",
                                   "proc_benpast:vig_vaccination_statusIs vaccinated",
                                   "vig_volunteer_workDoes volunteer work:proc_benpast",
                                   "vig_childrenHas children:proc_benfut",
                                   "proc_lifeq:vig_disabilityHas a disability",
                                   "vig_weightOverweight:proc_lifeq"
                                   ),
                        labels = c("50% chance of survival x Maximize prognosis",
                                   "80% chance of survival x Maximize prognosis",
                                   "50% chance of survival x Sickest first",
                                   "80% chance of survival x Sickest first",
                                   "50 years old x Youngest first",
                                   "75 years old x Youngest first",
                                   "Is already ventilated x First Come, first served",
                                   "Is vaccinated x Benefit in the past",
                                   "Does volunteer work x Benefit in the past",
                                   "Has children x Benefit in the future",
                                   "Has a disability x Life quality",
                                   "Is overweight x Life quality")
                        ),
          eff = x97_5_percent - ((x97_5_percent - x2_5_percent) / 2),
          attr = fct_rev(attr)
          ) %>% 
  ggplot(mapping = aes(x = attr,
                       y = eff,
                       ymin = x2_5_percent,
                       ymax = x97_5_percent
                       )
         ) +
    geom_bar(stat = "identity",
             fill = "#EB8019") + 
    geom_errorbar(width = 0.35,) +
    geom_hline(yintercept = 0,
               linetype = "dashed") +
    labs(y = "Interaction effects",
         x = "",
         title = "Plot c with numeric values") +
    coord_flip() +
    theme_minimal() +
    theme(text = element_text(family = "serif"),
          plot.title.position = "plot"
          )


```

Corresponding regression table:

```{r}
triage_data_clean %>% 
   filter(vig_set <= 5) %>% 
  lmer(formula = vig_choice ~ vig_weight * proc_lifeq + vig_age * proc_young + vig_chance_of_survival_with_ventilation * proc_maxprog + vig_chance_of_survival_with_ventilation * proc_sick + vig_ventilation_status * proc_fcfs + vig_children * proc_benfut + vig_disability * proc_lifeq + vig_volunteer_work * proc_benpast + vig_vaccination_status * proc_benpast + (1|id),
       data = .) %>% 
  summary()
```

# Sample

```{r}
triage_data_clean %>% 
  select("id","age") %>% 
  distinct() %>% 
  summarise(age_mean = mean(age, na.rm = T),
            age_sd = sd(age, na.rm = T)
            )

triage_data_clean %>% 
  select("id","educ") %>% 
  distinct() %>% 
  summarise(educ_mean = mean(educ, na.rm = T),
            educ_sd = sd(educ, na.rm = T)
            )

triage_data_clean %>% 
  select("id","gender") %>% 
  distinct() %>% 
  group_by(gender) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(prop = n/sum(n))

triage_data_clean %>% 
  select("id","cntry_live") %>% 
  distinct() %>% 
  mutate(cntry_live = countrycode(cntry_live,
                                  origin = "country.name.de",
                                  destination = "country.name.en"
                                  )
         ) %>%
  group_by(cntry_live) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(prop = n/sum(n)) %>% 
  distinct() %>% 
  print()
```



